---
title: "A1_TRAN_20286689.1"
output: html_document
date: "2025-01-07"
---

#Load all the packages that use for the assignment

```{r}
library(dplyr)
```

```{r}
library(ggplot2)
```

#Revise the data

```{r}
data <- read.csv("measurements.csv")
```

#Check for the data head

```{r}
head(data)
```

#To filter out the value that does not relate to the data

```{r}
data <- data %>%
  filter(!grepl("<<<<<<<|=======|>>>>>>>", Species))
```

#Check for the data again

```{r}
print(data)
```

#To arrage the table

```{r}
data2 <- data %>%
  arrange(Species, Observer, Volume)
```

#Check the new table head

```{r}

head(data2)
```

#To calculate the average volume of each species:

```{r}
averagevol <- data %>%
  group_by(Species) %>%
  summarise(Average_Volume = mean(Volume, na.rm = TRUE))
```

#To display the average volume of each species

```{r}
averagevol 
```

#To count the number of observations (i.e. rows) for each combination of species and observer

```{r}
obscount <- data %>%
  group_by(Species, Observer) %>%
  summarise(Count = n(), .groups = "drop")
```

#Display the table

```{r}
obscount
```

#Create a box plot comparing limb volume distributions for each species using ggplot:

```{r}
ggplot(data2, aes(x = Species, y = Volume)) +
  geom_boxplot() +
  xlab("Species") +
  ylab("Limb's Volume") +
  ggtitle("Distribution of limb volume by species") +
  theme_minimal()
```

Figure 1: This box plot displays the limb volume distrubution across species. The boxes represent the interquartile range (IQR) with the horizontal line inside each box indicating the median limb volume. The x-axis represents limb volume, while the y-axis represents the species

#Create a box plot comparing limb volume distributions for each species

```{r}
ggplot(data, aes(x = Volume)) +
  geom_histogram(binwidth = 30, color = "blue") +
  facet_wrap(~Species, scales = "free_y") +
  xlab("Limb's Volume") +
  ylab("Frequency") +
  ggtitle("Frequency histograms of limb volume by species") +
  theme_minimal()
```

Figure 2: This panel shows the frequency histograms of limb volumes for each species. Each panel represents a different species, showing the distribution of limb volumes. The x-axis represents limb volume, while the y-axis represents the frequency of observations.
